Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2022-11-27 beap_pres_dec2022/beap_pres_dec.tex
Nov 27 - updated beap presentation

@@

@@

	%SLIDE 6 LCRs are hypermutable
	\begin{frame}{LCR's are Hypermutable }

	%SLIDE 7 - Mechanisms of LCR Evolution
	\begin{frame}{Proposed Mechanisms of LCR Evolution }

@@

	%Slide 13 - Here we put MY version of the algorithm - We could also put these on the same slide and just compare! SLIDE 14 AND 15
	\begin{frame}{ABC-MCMC Algorithm - MY VERSION}

		\begin{enumerate}
			\item 
			\item
			\item
			\item
			\item
		\end{enumerate}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
	\begin{frame}{Simulation Step}

>>>>

%Trying this out for captions
\setbeamertemplate{caption}{%
	\begin{beamercolorbox}[wd=.5\columnwidth, sep=.2ex]{block body}\insertcaption%
	\end{beamercolorbox}%
}

@@

% Bibliography stuff
\usepackage[natbib=true, sorting=nyt, style=authoryear-comp]{biblatex}
\addbibresource{ABC1.bib}

%Extra packages
\usepackage{makecell}

@@

	%SLIDE 6 LCRs are hypermutable
	% Maybe change the lines from the fly to dashed - as per photo Lauren Sent
	\begin{frame}{LCR's are Hypermutable }

		\begin{center}	
		\includegraphics[width=8cm, height=3cm]{drosophila.png}
		\end{center}

		\begin{center}	
		\begin{tabular}{|cccc|}
			\hline
			\makecell{\textbf{mam} \\ \textbf{domain}} & \textbf{Size (bp)} & \makecell{\textbf{Amino Acid} \\ \textbf{Substitutions}} & \makecell{\textbf{Amino Acid/} \\ \textbf{Total Substitutions}}  \\ 
			\hline
			Unique & 933 & 26 & 0.15\\ 
			\hline
			Repetitive & 810 & 47 & 0.42\\ 
			\hline
		\end{tabular}\newline\newline
		\end{center}

	%\footer{\tiny\citep{newfeld1991interspecific}}
	\footnotetext[1]{\tiny\cite{newfeld1991interspecific}}	
	\end{frame}

	%SLIDE 7 - Mechanisms of LCR Evolution
	\begin{frame}{Proposed Mechanisms of LCR Evolution}
		\textit{1. Polymerase Slippage/Slipped Strand Mispairing}
		\begin{columns}

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage2.png} \\~\\
				\caption{\centering Polymerase Slips Forward}
			\end{figure}

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage1.png} \\~\\
				\caption{\centering Polymerase Slips Backwards}
			\end{figure}

		\end{columns}

	\footnotetext[2]{\tiny\cite{levinson1987slipped,sehn2015insertions}}
	\end{frame}

	%SLIDE 8 - Mechanisms of LCR Evolution
	\begin{frame}{Proposed Mechanisms of LCR Evolution}
		\textit{2. Unequal Recombination} \newline\newline

		\begin{figure}
			\includegraphics[width=8cm, height=1.8cm]{unequal.png} \\~\\
		\end{figure}

	\footnotetext[3]{\tiny\cite{levinson1987slipped,sehn2015insertions}}	
	\end{frame}

@@

	%Slide 13 - Here we put MY version of the algorithm - We could also put these on the same slide and just compare! SLIDE 14 AND 15
	%Should I put the equation for calculating distance in this slide? or at the end in the appendix idk yet.
	\begin{frame}{MCMC for ABC: Modified Algorithm}

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to the normal distribution
			\item Create a random protein sequence and mutate over many generations using $\theta'$ to generate simulated Dataset $D'$
			\item Calculate summary statistics for simulated dataset $D'$ 
			\item If $d(S',S) \le \epsilon$, go to next step, otherwise stay at $\theta$ and return to 1
			\item Accept $\theta'$ with probability ?? Ask Brian ab this again lol
			\item Return to step 1
		\end{enumerate}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
	\begin{frame}{Simulation Step - MAYBE}
